基于Lab色彩空间的太阳黑子手绘图背景提取方法

### 2017-01-13 paper/paper.tex
修改英文摘要

\textbf{Abstract: }Sunspots drawings，a traditional way of recording sunspots activities, is meaningful to research the sunspot's long-term movement regularity. What's more, background extraction is an important step to process hand-drawings digitally by computer. In order to solve the problem, a background subtraction method based on Lab color space is proposed. At first, it sections a and b color samples based on k-means clustering under Lab color space. Then analyzing clustering result and extracting background pixels and foreground pixels directly by discrimination function instead of clustering. The segmentation results show that the method can extract the printing part and hand-draw part quickly and accurately.

>>>>

\textbf{Abstract: }Sunspots drawings is a traditional way of recording sunspots activities. Digitization of the drawings help the long-term storage of the data and the research of it. Background extraction is an important step in the process of digitization. For this problem, we developed a rapid background extraction method based on Lab color space. In this method, we perform two-class K-means cluster for the $a$, $b$ component of Lab color space on the drawings. The cluster result shows that the background and handdrawing part are clustered into two class accurately. For mass drawings background extraction, we only select a part of drawings perform the aformentioned cluster, then apply their result on other drawings. Experiment result shows that this method enormously speed up the time of processing and guaranteed the accuracy at the same time.
